### 2022-06-05 paper/introduction.tex
update paper (introduction)

%% intro
Surface normal inference from a single view deals with the task of object surface orientation estimation. It has many practical applications, such as augmented reality and robotics.

>>>>

%%%%%%%%%%%%%%%%%%%% intro %%%%%%%%%%%%%%%%%%%%

%% What is surface normal
\section{Introduction}

Normal indicates the direction of a plane. In 3D coordinate systems, a normal is a vector, which perpendicular to the corresponding plane. Since only the direction property of a normal is demanded, the length is meaningless, thus the normal can be represented as an unit vector. In this case, each axis in range $ [-1,1] $. Therefore, for a polygon, the direction of each plane can be represented by its normal.

%% why surface normal is important

Surface normal has many practical applications, such as augmented reality and robotics. In these applications, normal is an important basic property of object surface. Some rendering tasks such as surface reconstruction, image registration, shading, etc, they all required surface normal as one of the inputs.

%% Surface normal from point cloud
Objects are usually captured by cameras, which provided as a single view scene with RGB colors. Some camera can also record the depth map at the same time. The depth can be converted to 3D vertices from image space. Therefore, the object in 3D space is usually represented as a point cloud. In this case, normals can not be calculated precisely since the planes of each point is unknown.

### 2022-06-05 paper/related_work.tex
update paper (introduction)

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{./ref/u-net-illustration-correct-scale2}
	\caption{U-net architecture (example for 32x32 pixels in the lowest resolution). Each blue box corresponds to a multi-channel feature map. The number of channels is denoted on top of the box. The x-y-size is provided at the lower left edge of the box. White boxes represent copied feature maps. The arrows denote the different operations.
	}
	\label{fig:u-net}
\end{figure}

>>>>

From considering neighborhoods in the same plane then using PCA for estimation to recently deep learning based methods, the task of surface normal inference is also been well studied in last 30 years.

@@

%%\begin{figure}[!h]
%%	\centering
%%	\includegraphics[width=\textwidth]{./ref/u-net-illustration-correct-scale2}
%%	\caption{U-net architecture (example for 32x32 pixels in the lowest resolution). Each blue box corresponds to a multi-channel feature map. The number of channels is denoted on top of the box. The x-y-size is provided at the lower left edge of the box. White boxes represent copied feature maps. The arrows denote the different operations.
%%	}
%%	\label{fig:u-net}
%% \end{figure}
